A thesis draft

### 2018-11-28 res/sections/40-FutureWork.tex
Fix future work

The realization of this architecture proposal is not finished yet. Indeed, a lot
of functionalities could be implemented and new components coul be added. We are
now going to see possible future additions to improve the system.

@@

Another security aspect which is important to provide is the isolation between
the network slices. This isolation, in our implementation, should be achieved
clearly identifing sets of nodes (the different slices) and restricting their
possibility to talk and interact with the other sets. This kind of restrinction
should be achieved using different group Policy through Kubernetes.

@@

A single Kubernetes cluster presents limitations in terms of number of nodes
available on a single cluster and regarding the geographical position of this
nodes. Indeed, nodes in a cluster should be located or in the same network or
geographically closer to each other, in order to ensure show latences between
data exchange and Pods communications. An available solution, introduced in
version 1.9 of Kubernetes, is the possibility to create federated Kubernetes
cluster. This solution ensures a proper division between groups of nodes, and
the possibility to ensure better performances creating cluster with nodes closer
to each other. Unfortunatly, we werent able to create a proper Kubernetes
federation. On of the reason was related the current immaturity of the project,
that could have created and instable cluster federation.

@@

The importance of having NS services updated as smooth as possible is without 
doubts a feature that would ensure a continue service availability avoiding its 
disruption. This kind of approach, though, requires particular attention about 
keeping the current connections alive. This means at least keeping the old 
chain up while deploying the new one, and gradefully redirect all the 
new traffic from the chain to replace, until none is left. Only after this 
operation, the old chain definition can be completely decomissioned and the 
related VNFs removed. In our current implementation, the NS update 
functionality relies on a simpler approach: when an update gets ordered, 
Kubernetes gets instructed to remove the old chain and deploy the new one. 
Meanwhile, all the Roulette controllers get updated with the new NS route. The 
back of the medal of this soulution is, while it keeps the sistem implementation 
simpler, that packets current travelling along the old NS could be lost during 
the chain updating.

>>>>

The realization of this architecture proposal is not finished yet. Indeed, a lot
of functionalities could be implemented and new components could be added. We
are now going to see possible future additions to improve the system.

@@

Another security aspect which is important to provide is the isolation between
network slices. This isolation, in our implementation, should be achieved
clearly identifing sets of nodes (the different slices) and restricting their
possibility to talk and interact with the other sets. This kind of restrinction
should be achieved using different policy groups through Kubernetes.

@@

A single Kubernetes cluster presents limitations in terms of number of nodes
available on a single cluster and regarding the geographical position of this
nodes. Indeed, nodes in a cluster should be located or in the same network or
geographically closer to each other, in order to ensure low latences between
data exchange and Pods communications. An available solution, introduced in
version 1.9 of Kubernetes, is the possibility to create federated Kubernetes
clusters. This solution ensures a proper division between groups of nodes, and
the possibility to ensure better performances creating clusters only with nodes
closer to each other. Unfortunatly, we were not able to create a proper
Kubernetes federation. One of the main reasons was related the current
immaturity of the project, that could have created and instable cluster
federation.

@@

The importance of having NS services updated as smooth as possible is without
doubts a feature that would ensure a continue service availability avoiding its
disruption. This kind of approach, though, requires particular attention about
keeping the current connections alive. This means at least keeping the old chain
up while deploying the new one, and gracefully redirect all the new traffic from
the chain to replace, until none is left. Only after this operation, the old
chain definition can be completely decomissioned and the related VNFs removed.
In our current implementation, the NS update functionality relies on a simpler
approach: when an update gets ordered, Kubernetes gets instructed to remove the
old chain and deploy the new one. Meanwhile, all the Roulette controllers get
updated with the new NS route. While this keeps the system implementation
simpler the back of the medal of this soulution is that packets currently
travelling along the old NS could be lost during the chain update.
